Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-04-09 paper/manuscript_bioRxiv.tex
added _bioRxiv_ version (no _PNAS_ labels)

\documentclass[9pt,twocolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

@@

\acknow{We thank Sarah Hilton, Hugh Haddox, and Sidney Bell for helpful discussions about data analysis and we thank Richard Neher for sharing analysis code and providing helpful comments on an initial version of the manuscript.
We thank the Fred Hutch Genomics Core for performing the Illumina deep sequencing.
This work was supported by grant R01 AI127893 from the NIAID of the NIH to JDB and TB and grant U19 AI117891 to TB.
JML was supported in part by the Center for Inference and Dynamics of Infectious Diseases (CIDID), which is funded by grant U54GM111274 from the NIGMS of the NIH.
The research of JDB is supported in part by a Faculty Scholar grant from the Howard Hughes Medical Institute and the Simons Foundation, and a Burroughs Wellcome Young Investigator in the Pathogenesis of Infectious Diseases grant.
TB is a Pew Biomedical Scholar and is supported by NIH R35 GM119774.
}

>>>>

\documentclass[9pt,twocolumn,twoside]{pnas-new-for-biorxiv}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

@@

\acknow{We thank Sarah Hilton, Hugh Haddox, and Sidney Bell for helpful discussions about data analysis, and Richard Neher for sharing analysis code and providing helpful comments on the manuscript.
We thank the Fred Hutch Genomics Core for performing the Illumina deep sequencing.
This work was supported by grant R01 AI127893 from the NIAID of the NIH to JDB and TB and grant U19 AI117891 to TB.
JML was supported in part by the Center for Inference and Dynamics of Infectious Diseases (CIDID), which is funded by grant U54GM111274 from the NIGMS of the NIH.
The research of JDB is supported in part by a Faculty Scholar grant from the Howard Hughes Medical Institute and the Simons Foundation, and a Burroughs Wellcome Young Investigator in the Pathogenesis of Infectious Diseases grant.
TB is a Pew Biomedical Scholar and is supported by NIH R35 GM119774.
}
